Synthesis of Rules for Network Intrusion Detection

### 2019-10-20 paper/paper.tex
pass on technique

\begin{document}
%
\title{Synthesis of Rules for Network Intrusion Detection}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Lucas Alcantara\inst{1}\Comment{\orcidID{0000-1111-2222-3333}} \and
Guilherme Padilha\inst{1}\Comment{\orcidID{1111-2222-3333-4444}} \and
Marcelo d'Amorim\inst{1}\Comment{\orcidID{0000-0002-1323-8769}}}
%
\authorrunning{Alcantara et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Federal University of Pernambuco (UFPE), Recife, Brazil\\
\email{\{lama,ghps,damorim\}@cin.ufpe.br}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Network Intrusion Detection Systems (\nids{}) are a popular mechanism
used by system administrators to defend against network attacks. These
systems monitor the network traffic and flag suspicious network
behavior. Signature-based \nids\ do that by checking the network
traffic against a pre-defined set of rules, which can become obsolete
as attackers learn new strategies to circumvent existing defenses.
This paper proposes \tname{}, a technique that automatically
synthesizes \nids\ rules from positive and negative examples (\ie{},
malicious and benign traffic). \tname{} formulates synthesis as an
optimization problem whose candidate solutions are rules that
maximizes the captured the positive traffic and minimizes the captured
negative traffic. \tname{} bootstraps the search with candidate
solutions that use data from the payload of the malicious message and
produces optimal rule candidates on output. We evaluated \tname{} on a
diverse set of attacks. Results indicate that \Fix{...}

@@

The SYN Flood attack exploits a vulnerability in the TCP/IP handshake
to establish a TCP connection~\cite{cloudfare-synflood}. The handshake
works as follows in normal circumstances. First, a client sends a SYN
packet to the server, requesting a connection. Second, the server
responds with a SYN-ACK packet to the client. Third, the client
responds with an ACK message and the connection is established. Aware
of the protocol, an attacker sends multiple SYN packets to different
ports of a server, often using fake IP addresses. Then, after the
server responds with a SYN-ACK packet, the client keeps sending other
SYN to avoid the connection to time out. Without proper protection,
the server accepts these malicious requests and eventually legitimate
requests cannot be satisfied due to resource exhaustion.

Figure~\ref{fig:synflood-example} shows a Suricata rule to capture
this attack. The critical parts are the option \CodeIn{flags: S,12},
which identifies a SYN packet and the option \CodeIn{threshold: type
  both, track by\_dst, count 5000, seconds 5}, indicating that a high
volume of such packets should be requested in a short period of
time.\Mar{please, explain the other fields}

@@

\section{Approach}

@@

\tname{} is a search-based approach that uses positive and negative
network examples to synthesize signature-based NIDS rules, such as
those from Snort and Suricata.

The technique synthesizes rules in two steps. First, it produces a
potentially overspecified rule that captures the negative example
provided on input. Then, it uses positive examples to eliminate
unnecessary options from the rule. The goal of \tname\ is to create a
rule that only captures the negative traffic.

>>>>

\begin{document}
%
\title{Synthesis of Rules for Network Intrusion Detection}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Lucas Alcantara\Comment{\inst{1}}\Comment{\orcidID{0000-1111-2222-3333}} \and
Guilherme Padilha\Comment{\inst{1}}\Comment{\orcidID{1111-2222-3333-4444}} \and
Marcelo d'Amorim\Comment{\orcidID{0000-0002-1323-8769}}}
%
\authorrunning{Alcantara et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Federal University of Pernambuco (UFPE), Recife, Brazil\\
\email{\{lama,ghps,damorim\}@cin.ufpe.br}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Network Intrusion Detection Systems (\nids{}) are a popular mechanism
used by system administrators to defend against network attacks. These
systems monitor the network traffic and flag suspicious network
behavior. Signature-based \nids\ do that by checking the network
traffic against a pre-defined set of rules, which can become obsolete
as attackers learn new strategies to circumvent existing defenses.
This paper proposes \tname{}, a technique that automatically
synthesizes \nids\ rules from positive and negative examples (\ie{},
malicious and benign traffic). \tname{} formulates synthesis as an
optimization problem whose candidate solutions are rules that
maximizes the captured the positive traffic and minimizes the captured
negative traffic. \tname{} bootstraps the search with candidate
solutions that use data from the payload of the malicious message and
produces optimal rule candidates on output. We evaluated \tname{} on a
diverse set of attacks. Results indicate that \Fix{...}

@@

The SYN Flood attack exploits a vulnerability in the TCP/IP handshake
to establish a TCP connection~\cite{cloudfare-synflood}. The handshake
works as follows in normal circumstances. First, a client sends a SYN
packet to the server, requesting a connection. Second, the server
responds with a SYN-ACK packet to the client. Third, the client
responds with an ACK message and the connection is established. Aware
of the protocol, an attacker sends multiple SYN packets to different
ports of a server, often using fake IP addresses. Then, after the
server responds with a SYN-ACK packet, the client keeps sending other
SYN packets to avoid the connection to time out. Without proper
protection, the server accepts these malicious requests and eventually
legitimate requests cannot be satisfied due to resource exhaustion.
Figure~\ref{fig:synflood-example} shows a Suricata rule to capture
this attack. The critical parts appear in bold---the option
\CodeIn{flags: S,12}, which identifies a SYN packet and the option
\CodeIn{threshold: type both, track by\_dst, count 5000, seconds 5},
indicating that a high volume of such packets should be requested in a
short period of time.

%\Mar{please, explain the other fields}

@@

\section{Technique}

@@

\tname{} is a search-based approach that uses positive and negative
examples to synthesize signature-based NIDS rules, such as those from
Snort and Suricata. The technique synthesizes rules in two
steps. First, \tname{} produces a potentially overspecified rule that
captures the malicious traffic provided on input. The rule obtained in
this stage can also capture benign traffic. In this step,
\tname\ \emph{maximizes} the number of properties in the rule that
captures the positive traffic. It extracts the tokens from the payload
of the positive traffic (\ie{}, malicious traffic) and add them as
content properties (see Section \Fix{xxx}). Furthermore, it searches
for additional properties satisfied by the positive traffic. Any
subset of properties found in this stage, by construction, captures
the positive traffic. In the second step, \tname{} uses negative
examples to \emph{minimize} the rule, discarding unnecessary
options. The goal of \tname\ is to create a rule that only captures
the positive traffic. The search is optimal (\ie{}, we reach this
goal) if no benign message is captured during the minimization step.

\Fix{...............estou aqui}
